Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-10-24 paper/main.tex
explain more clearly what we are doing in the introductory part

% --------------------------------------------------------------------------------------------------
\subsection{Parameter Estimation}
\label{section:parameter-estimation}
In order to effectively estimate the parameters of our model, we need to set up a loss function
which can be minimized. In doing so, we hope to identify all parameters, given relevant experimental data.
We utilize the preceding algorithms to extract data from cell-masks, simulate from an initial state
and then compare both results.
The cell-masks are easily obtainable by either using existing segmentation
tools~\cite{Cutler2022,Stringer2020,Hardo2022} or manually annotating microscopic image series.

\textbf{Du solltest hier erwähnen, dass du die Parameter per Bakterium fittest und nicht globale Parameter.}

>>>>

% --------------------------------------------------------------------------------------------------
\subsection{Parameter Estimation}
\label{section:parameter-estimation}
In order to effectively estimate the parameters of our model, we need to set up a cost function
which can be minimized.
In doing so, we hope to identify all parameters, given relevant experimental data.
Parameters may be defined as global ones, which are identical across all cells or individual per
cell.
We utilize the preceding algorithms to extract data from cell-masks, simulate from an initial state
and then compare both results.
The cell-masks are easily obtainable by either using existing segmentation
tools~\cite{Cutler2022,Stringer2020,Hardo2022} or manually annotating microscopic image series.

\textbf{Du solltest hier erwähnen, dass du die Parameter per Bakterium fittest und nicht globale Parameter.}
\textit{Tue ich aber nicht grundsätzlich. Es gibt globale und individuelle parameter; also ein "mixed approach". Ich habe aber einen Hinweis eingefügt.}
